### 2016-04-07 Projects/DelCo_2012/Report/DelCo_2012.tex
filled in some gaps in discussion on gas cooling

In each gas cooling experiment, the same mass flow rate of water was used for both the plain water stream and the CAF stream. Typically the volumetric flow rate of water was 120 gpm. The density of water is 8.3 lbs/gal    therefore the mass flow rate was    .  The average time of flow was 15~s, therefore a total of X kg of water was introduced into each gas cooling experiment. When a CAFs stream was used it contained 0.3\% foam concentration by volume, check density of foam concentrate   point being mostly water.  Also calc the mass of air in the stream.

>>>>

In each gas cooling experiment, the same mass flow rate of water was used for both the plain water stream and the CAF stream. Typically the volumetric flow rate of water was 7.57~L/s (120~gpm). The density of water is 1000~kg/m$^3$ (8.3~lb/gal), therefore the mass flow rate was 7.57~kg/s (16.7~lb/s).  The average time of flow was 15~s, therefore a total of 114~kg (251~lb) of water was introduced into each gas cooling experiment. When a CAFs stream was used it contained 0.3\% foam concentration by volume, check density of foam concentrate   point being mostly water.  Also calc the mass of air in the stream.
